\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://linkedin.com/in/jasonpetri/}{\Large Jason F. Petri}} & \href{mailto:jasonfpetri@outlook.com}{jasonfpetri@outlook.com}\\
  \href{http://linkedin.com/in/jasonpetri/}{linkedin.com/in/jasonpetri} & \href{http://github.com/jptree}{github.com/jptree} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Texas}{Austin, TX}
      {Master of Science in Business Analytics}{May 2021}
    \resumeSubheading
      {University of Akron}{Akron, OH}
      {Bachelor of Business Administration in Financial Management}{May 2020}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {KeyBanc Capital Markets}{Cleveland, OH}
      {Quantitative Analyst}{July 2021 - Present}
      \resumeItemListStart
        \resumeItem{Trading Application}
            {Built a realtime fixed income trading application using TypeScript, React, AgGrid, Kafka, and FastAPI that supports thousands of updates per second, tens of millions of messages per day, matrix pricing, formulas, and 5 concurrent corporate bond traders to manage risk and respond to RFQs.}
        \resumeItem{Pricing Engine}
            {Built a microservice API with Refinitiv bond fundamental data, QuantLib, and BPIPE treasury curves to support over 3000 calculations per second of duration, yield, price, net present value, and yield-to-worst for investment grade corporate bonds.}
        \resumeItem{Spread Modeling}
            {Generated model features in BigQuery from various sources with window functions to detrend and predict g-spread dynamics using Random Forest models. Deployed models in real-time trading and analytics.}
        \resumeItem{Visual Analytics}
            {Deployed 8 Streamlit, React, or Tableau applications with over 20 daily active users improving reporting accuracy to regulators and clients.}
        \resumeItem{Vendor Management}
          {Consulted with vendors to gather firewall, connectivity, public/private key details from OneTick, Refinitiv, Bloomberg, and MarketAxess to enable connectivity between internal cloud environments and vendor APIs, FIX engines, and data products.}
        \resumeItem{Data Transformation}
            {Productionized 11 ETL pipelines using Airflow, BigQuery, Cloud Storage, and Postgres.}
        \resumeItem{Unstructured Data}
          {Utilized BigQuery to produce weekly sell-side research products consisting of over 1100 unique companies from our terabyte-scale consumer transaction dataset.}
        \resumeItem{Trading Infrastructure}
          {Architected and wrote Java application to interface with MarketAxess FIX engine to send algorithmically-generated spread to benchmark levels for investment grade bonds. Streamed live positions and trade data from TOMS API.}
        \resumeItem{Cloud Migration}
            {Gathered requirements from internal team, designed, and implemented a cloud-native solution to promote usability and cost savings. Collaborated with internal technology teams to abide by security model for publicly available endpoints and data loss prevention initiatives.}
        \resumeItem{Generative Modeling}
            {Trained a generative adversarial network (GAN) with TensorFlow to simulate equity order flow data. Used synthetic data to backtest market impact models.}
        \resumeItem{Volatility Modeling}
            {Implemented equity volatility models and produced an automated Airflow job to store volatility estimations for our tradable universe. Used volatility models and Monte-Carlo simulations to estimate probability of limit order fills.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Dun \& Bradstreet Natural Language Processing}
      {Extracted mergers and acquisition activity details from news feeds using TensorFlow and feature vectors derived from large language models.}
    \resumeSubItem{Factor Modeling}
      {Constructed long-short portfolios on default probability and regressed returns to impute alpha.}
    \resumeSubItem{Portfolio Management Web Application}
      {Portfolio visualization tool to monitor live performance of University of Akron's student managed fund.}
    \resumeSubItem{Honors Thesis}
      {Analyzed country-linked ETFs and the influence of culture and governance on financial crash risk. Research resulted in a published work at an institution.}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \item{
            \textbf{Languages}{: Python, Javascript, Java, SQL}
      \hfill
    }
\item {
      \textbf{Technologies}{: BigQuery, Linux, Docker, git, TypeScript, React, Kafka, Redis, Flask}
}
\item {
      \textbf{Licenses}{: Securities Industry Essentials, Series 7}
}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
